---
title: "Assignment"
author: "Johann Wagner, u6958957"
date: "2023-08-25"
output:  
    html_document:
        toc: true
        toc_depth: 4
        theme: cosmo
        number_sections: false
        toc_float: true
        highlight: pygments
        fig_width: 8
        fig_height: 4
---

# **Setup and Configuration**

## Load in relevant packages

```{r Setup and Configuration, echo = FALSE}
# The tidyverse is a collection of R packages designed for data science.
# All packages share a similar design philosophy, grammar, and data structures.
# Tidyverse includes packages such as:
# ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, lubridate, and forcats.
### https://www.tidyverse.org/
library(tidyverse)

# To easily read in Excel into R.
### https://readxl.tidyverse.org/
library(readxl)
```

## Load in Movie data

```{r Data Loading}
PERSON <- read_xlsx("movies.xlsx",
  sheet = "PERSON"
)

MOVIE <- read_xlsx("movies.xlsx",
  sheet = "MOVIE"
)

RESTRICTION <- read_xlsx("movies.xlsx",
  sheet = "RESTRICTION"
)
```

# **Assignment Questions**

#### **Question 1:** How many persons were born after 1974 whose first name ends with 'e'? List that number.

```{r Question 1}
PERSON %>%
  mutate(
    first_name_last = first_name %>%
      str_sub(start = -1)
  ) %>%
  filter(
    year_born > 1974,
    first_name_last == "e"
  ) %>%
  count()
```

#### **Question 2:** Find the average run time of movie(s) which were produced before 1991 and categorised as 'PG-13' restriction in the USA. List the average as a decimal (round to two decimal places).

*Hint: in PostgreSQL, the function ROUND(x, n) can round x to n decimal places, e.g., if x=0.1129, then ROUND(x, 2) = 0.11.*

```{r Question 2}
MOVIE %>%
  full_join(
    RESTRICTION,
    join_by(title, production_year)
  ) %>%
  filter(
    production_year < 1991,
    description == "PG-13",
    country.y == "USA"
  ) %>%
  summarise(mean_run_time = mean(run_time))
```
